---
title: "Safe Use of Opioids - Concurrent Prescribing"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: cerulean
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(qicharts2)
library(lubridate)
library(highcharter)


```



```{r load-data}

cohort <- read_csv("cohort.csv") |> janitor::clean_names()
demographics <- read_csv("demographics.csv") |> janitor::clean_names()
readmissions <- read_csv("readmissions.csv") |> janitor::clean_names()
medications <- read_csv("medications.csv") |> janitor::clean_names()


cohort <- cohort |> 
  mutate(race_ethnicity = case_when(
    str_detect(ethnicity,"WHITE") ~ "White",
    str_detect(ethnicity,"BLACK|AFRICAN") ~ "Black or African American",
    str_detect(ethnicity,"HISPANIC|LATINO") ~ "Hispanic/Latino",
    str_detect(ethnicity,"ASIAN") ~ "Asian",
    str_detect(ethnicity,"DECLINED") ~ "Declined to Answer",
    str_detect(ethnicity,"OTHER") ~ "Other",
    T ~ "Unknown"
  ),
  multiple_meds_at_discharge = case_when(n_opioid_at_discharge > 1 ~ 1,
                                                n_opioid_at_discharge + n_benzo_at_discharge > 1 ~ 1,
                                                T ~ 0),
         year_of_discharge = floor_date(dischtime,"year")
)


readmissions_df <- readmissions |> 
  inner_join(cohort,by = c("hadm_id","subject_id")) |>
  group_by(year_of_discharge) |>
  summarise(
    readmissions = sum(readmission_ind),
    readmission_30_days = sum(readmission_30_days),
    readmission_60_days = sum(readmission_60_days),
    readmission_90_days = sum(readmission_90_days),
    n = n()
  )


multiple_meds_discharged <- cohort |> 
  group_by(year_of_discharge) |> 
  summarise(
    multiple_meds_at_discharge = sum(multiple_meds_at_discharge),
    n = n()
  )

```

Patient Details
======================================================================

Row 
-----------------------------------------------------------------------
### Unique Patient Admissions
```{r }

valueBox(value = nrow(cohort),color = "primary",icon = "fa-hospital-o")
```

### 30 days Readmissions  
```{r }

valueBox(value = sum(readmissions_df$readmission_30_days),color = "info", icon = "fa-ambulance")
```

### 60 days Readmissions 
```{r }

renderValueBox(valueBox(value = sum(readmissions_df$readmission_60_days),color = "success", icon = "fa-h-square"))
```


Row {data-width=650}
-----------------------------------------------------------------------

### Race and Ethnicity

```{r race}
paretochart(cohort$race_ethnicity,
            title = 'Pareto Chart of Race/Ethnicity',x.angle = 90)

```

### Gender
```{r age}
demographics |> count(gender) |> 
  hchart('column', hcaes(x = gender, y = n)) |> 
   hc_tooltip(formatter = JS("function(){
                  return (' #:' + this.point.n)
                  }")) |> 
    hc_title(text = "Breakdown by Gender") |> 
  hc_xAxis(title = list(text = "Gender")) |> 
  hc_yAxis(title = list(text = ""))
```

Count of Opioid at Discharge {data-navmenu="Process Measures"}
==================================================

Row 
-----------------------------------------------------------------------


### Average Count of Opioid Medications at Discharge {Xbar Chart}
```{r}
qic(year_of_discharge, n_opioid_at_discharge,
    data  = cohort,
    chart = 'xbar',
    title = "Average Count of Opioid Medications at Discharge {Xbar Chart}",
    ylab  = '# Count',
    xlab  = 'Year',
    show.grid = T,
    y.neg = F
    )


```


### Average Count of Opioid Medications at Discharge {MR Chart}
```{r}
qic(year_of_discharge, n_opioid_at_discharge,
    data  = cohort,
    chart = 'mr',
    title = "Average Count of Opioid Medications at Discharge {MR Chart}",
    ylab  = '# Count',
    xlab  = 'Year',
    show.grid = T,
    y.neg = F
    )

```

Count of Benzodiazepine at Discharge {data-navmenu="Process Measures"}
==================================================

Row 
-----------------------------------------------------------------------

### Average Count of Benzodiazepine Medications at Discharge {Xbar Chart}
```{r}

qic(year_of_discharge, n_benzo_at_discharge,
    data  = cohort,
    chart = 'xbar',
    title = "Average Count of Benzodiazepine Medications at Discharge {Xbar Chart}",
    ylab  = '# Count',
    xlab  = 'Year',
    show.grid = T, 
    y.neg = F)

```


### Average Count of Benzodiazepine Medications at Discharge {MR Chart}
```{r}

qic(year_of_discharge, n_benzo_at_discharge,
    data  = cohort,
    chart = 'mr',
    title = "Average Count of Benzodiazepine Medications at Discharge {MR Chart}",
    ylab  = '# Count',
    xlab  = 'Year',
    show.grid = T, 
    y.neg = F)

```


Rate of Multiple Medications at Discharge {data-navmenu="Process Measures"}
==================================================

### Rate of Multiple Medications at Discharge
```{r}

qic(year_of_discharge, multiple_meds_at_discharge, n,
    data      = multiple_meds_discharged,
    chart     = 'p',
    y.percent = TRUE,
    title     = 'Discharged With Multiple Medications {P chart}',
    caption = " Patients with more than one opioids OR \nat least one Opioid and One Benzodiazepine at discharge",
    show.grid = T,
    ylab      = NULL,
    xlab      = 'Year'
    )

```

Outcome Measures
=========================================================

### Readmissions Within 30 Days
```{r}


qic(year_of_discharge, readmission_30_days, n,
    data      = readmissions_df,
    chart     = 'p',
    y.percent = TRUE,
    title     = 'Readmissions Within 30 days {P Chart}',
    ylab      = NULL,
    show.grid = T,
    xlab      = 'Year'
)


```


